04_DESeq_sexes

### 2019-12-23 analysis/04_LDA.Rmd
better lda tables

```{r LDAplots}
#myshapes = c("hypothalamus" = 20,  "pituitary" = 17,  "gonads" = 15)

@@

LDA.hyp %>% distinct(treatment, predictedstage) %>%
  group_by(treatment) %>%
  summarize(predictedstages = str_c(predictedstage , collapse = ", "))

LDA.hyp %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n())

LDA.pit %>% distinct(treatment, predictedstage) %>%
  group_by(treatment) %>%
  summarize(predictedstages = str_c(predictedstage , collapse = ", "))

LDA.pit %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n())

LDA.gon %>% distinct(treatment, predictedstage) %>%
  group_by(treatment) %>%
  summarize(predictedstages = str_c(predictedstage , collapse = ", "))

LDA.gon %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n())
```

>>>>

```{r LDAplots}
library(kableExtra)
#myshapes = c("hypothalamus" = 20,  "pituitary" = 17,  "gonads" = 15)

@@

df1 <- LDA.hyp %>% distinct(treatment, predictedstage) %>%
  group_by(treatment) %>%
  summarize(predictedstages = str_c(predictedstage , collapse = ", ")) 
kable(df1)

df2 <- LDA.hyp %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n())
kable(df2)

df3 <- LDA.pit %>% distinct(treatment, predictedstage) %>%
  group_by(treatment) %>%
  summarize(predictedstages = str_c(predictedstage , collapse = ", "))
kable(df3)

df4  <- LDA.pit %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n())
kable(df4)

df5 <- LDA.gon %>% distinct(treatment, predictedstage) %>%
  group_by(treatment) %>%
  summarize(predictedstages = str_c(predictedstage , collapse = ", "))
kable(df5)

df6 <- LDA.gon %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n())
kable(df6)
```
